Lightweight Real-Time Feature Monitoring

### 2020-07-20 paper.tex
Paper done

In this thesis, we used the Jensen–Shannon Divergence (JSD) as a statistical test to measure the distance or divergence between our reference and target sliding window aggregation. We chose to use the JSD metric due to its simplicity and because it was used in previous work successfully \cite{SAMM}. We believe that future work comprises testing new distances in the literature. In particular, we believe the Wasserstein distance is worth trying next, and illustrate why with Figure \ref{fig:wasserteinvsjsd} and Table \ref{tbl:wassertein-vs-jsd}. 
\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.3]{figures/wasserstein-vs-jsd.pdf}
      \caption{Wassertein vs Jensen–Shannon distances}
      \label{fig:wasserteinvsjsd}
    \end{center}
\end{figure}
\begin{table}[!htb]
    \begin{center}
        \begin{tabular}{|c|c|c|c|}
        \hline
        \textbf{Distribution \#1} & \textbf{Distribution \#2} & \textbf{Wasserstein} & \textbf{JSD} \\ \hline
        a                         & a'                        & 2.0                         & 0.4451                         \\ \hline
        b                         & b'                        & 0.5                         & 0.4451                         \\ \hline
        \end{tabular}
    \end{center}
    \caption[Wasserstein and Jensen-Shannon divergences output comparison]{Wasserstein and Jensen-Shannon divergences for both distribution pairs}
    \label{tbl:wassertein-vs-jsd}
\end{table}
The Wasserstein distance measures the work required to transport the probability mass from one histogram to another. This measure will be larger the further way the probability mass is. In Figure \ref{fig:wasserteinvsjsd}, we show two pairs of histograms, \textit{Histogram (a)} paired with \textit{Histogram (a')} and \textit{Histogram (b)} paired with \textit{Histogram (b')}. Table \ref{tbl:wassertein-vs-jsd} shows the output values for both pairs by each divergence function. The JSD measure is the same for both cases, whereas the Wasserstein distance is larger for the first pair because the probability mass has to be transported further.

In this thesis, we had to deal with the multiple test problem and apply a multiple test correction. In our case, we used Holm-Bonferroni due to its simplicity and because it controls the family-wise error rate with larger power than some other methods (thus providing a good trade-off between simplicity and power). There are many other multiple test correction methods, and we leave the testing of each as future work.

>>>>

In this paper, we used the Jensen–Shannon Divergence (JSD) as a statistical test to measure the distance or divergence between our reference and target sliding window aggregation. We chose to use the JSD metric due to its simplicity and because it was used in previous work successfully \cite{SAMM}. We believe that future work comprises testing new distances in the literature. In particular, we believe the Wasserstein distance is worth trying next, and illustrate why with Figure \ref{fig:wasserteinvsjsd} and Table \ref{tbl:wassertein-vs-jsd}. 
\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.3]{figures/wasserstein-vs-jsd.pdf}
      \caption{Wassertein vs Jensen–Shannon distances}
      \label{fig:wasserteinvsjsd}
    \end{center}
\end{figure}
\begin{table}[!htb]
    \begin{center}
        \begin{tabular}{|c|c|c|c|}
        \hline
        \textbf{Distribution \#1} & \textbf{Distribution \#2} & \textbf{Wasserstein} & \textbf{JSD} \\ \hline
        a                         & a'                        & 2.0                         & 0.4451                         \\ \hline
        b                         & b'                        & 0.5                         & 0.4451                         \\ \hline
        \end{tabular}
    \end{center}
    \caption[Wasserstein and Jensen-Shannon divergences output comparison]{Wasserstein and Jensen-Shannon divergences for both distribution pairs}
    \label{tbl:wassertein-vs-jsd}
\end{table}
The Wasserstein distance measures the work required to transport the probability mass from one histogram to another. This measure will be larger the further way the probability mass is. In Figure \ref{fig:wasserteinvsjsd}, we show two pairs of histograms, \textit{Histogram (a)} paired with \textit{Histogram (a')} and \textit{Histogram (b)} paired with \textit{Histogram (b')}. Table \ref{tbl:wassertein-vs-jsd} shows the output values for both pairs by each divergence function. The JSD measure is the same for both cases, whereas the Wasserstein distance is larger for the first pair because the probability mass has to be transported further.

In our method, we had to deal with the multiple test problem and apply a multiple test correction. In our case, we used Holm-Bonferroni due to its simplicity and because it controls the family-wise error rate with larger power than some other methods (thus providing a good trade-off between simplicity and power). There are many other multiple test correction methods, and we leave the testing of each as future work.
